\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Anupam Kumar}} & Email: \href{mailto:anupamkumar0401@gmail.com}{anupamkumar0401@gmail.com}\\
  {Software Developer} & Mobile:~~~+91-6202684631 \\
  {}{} & \href{https://github.com/Anupam0401}{GitHub } \textbar{} \href{https://www.linkedin.com/in/anupam-kumar-17b0b9210/}{LinkedIn} \\
\end{tabular*}

%-----------EDUCATION-----------------
\vspace{5pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Bhilai}{Raipur, Chhatisgarh}
      {Bachelor of Technology - Computer Science;  CGPA: 8.66}{July 2019 - April 2023}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:}  Data Structures and Algorithms, OOPS, Operating Systems, Database Management System, Machine Learning}}}
    \resumeSubHeadingListEnd

\vspace{5pt}
\section{Technical Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages and Frameworks}{~JAVA, Kotlin, C++, Python, SpringBoot}
	\resumeSubItem{Databases and Messaging}{~~~~SQL, PostgreSQL, MySQL, Kafka, MongoDB}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Git, Shell, Docker, Kubernetes, Prometheus, Grafana, JUnit, GraphQL, Gradle, Maven}
	\resumeSubItem{Interests}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Low Level and High Level Design, Microservice Architecture}

\resumeSubHeadingListEnd
\vspace{5pt}
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{\href{https://navi.com/}{Navi Technologies}}{On-site (Bangalore)}
    {Software Developer (Full-time) \textbar{} Team: Personal Loan \textbar{} Language: Java, Kotlin}
    {July 2023 - present}
    \resumeItemListStart
    \resumeItem {Processing Fee Introduction}{Led the end-to-end backend delivery of introducing Processing in Personal Loan journey across three different operations, direct contribution of ₹1CR per day in revenue}
    \resumeItem {Revamped Loan Journeys}{Redesigned Personal Loan Repeat and Top-Up flows, including \textbf{Offer Generation}, \textbf{Mandate}, and \textbf{Disbursement}. Increased approval-to-disbursal rates (24\% → 29\%, 14\% → 25\%) and daily gross disbursal by \textbf{33.5\%} (₹17.6 Cr → ₹23.5 Cr) and \textbf{26.6\%} (₹10.5 Cr → ₹13.3 Cr), respectively.}
    \resumeItem {EMI Date Standardization}{Streamlined EMI date logic by consolidating to 4 dates and integrating with a dedicated decisioning service. Revamped API workflows, streamlining processes and eliminating redundant code, resulting in significantly \textbf{enhanced collection efficiency}}.
    \resumeItem {Comms in Vernacular Languages}{Implemented multi-language communication for disbursement success and loan closure in \textbf{10 vernacular languages}. Optimized workflows, reduced redundant read calls, and added document links to SMS, enhancing customer satisfaction and experience.}
    \resumeItem {OKYC Integration}{Implemented \textbf{Aadhaar and PAN verification} using Digilocker, increasing KYC completion rate by \textbf{10.2\%} and reducing completion time.}
    \resumeItem {Workflow Optimization}{Automated QA processes, reducing time from \textbf{10 minutes to less than 1 minute}, and simplified KYC verification for faster onboarding.}
    % \resumeItem {Legacy Code Refactoring}{Optimized \textbf{APIs} for underwriting, validations, and document generation, improving system \textbf{reliability and scalability}.}
    \resumeItem {On-Call Support}{Resolved high-priority customer issues during on-call rotations, ensuring minimal downtime and consistent \textbf{service reliability}.}
\resumeItemListEnd

\vspace{2pt}
    \resumeSubheading
		{\href{https://www.click2cloud.com/}{Click 2 Cloud}}{On-site (Bhilai)}
		{SDE Intern (Full Time) \textbar{} Language: Python, SQL}{May 2022 - July 2022}
		\resumeItemListStart
        \resumeItem {Cloud Migration}{Executed the migration of cloud infrastructure from Microsoft Azure to Google BigQuery.}
        \resumeItem {Key-Value Extraction}{Implemented algorithms to extract key-value pairs from diverse document formats.}
        \resumeItem {SQL Injection Analysis}{Implemented techniques for information retrieval through SQL injection analysis and testing.}
		\resumeItemListEnd
\vspace{-5pt}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Network Software Monitoring Tool}{Smart India Hackathon Project \textbar{} \href{https://drive.google.com/file/d/1qiZesrt7hEhPYErSuQzsLiEyiWKDYhZi/view?usp=sharing}{Design document}}
\vspace{-2pt}
\begin{itemize}
\item Developed a \textbf{tool} to monitor and regulate \textbf{software installations} on network devices.  
\vspace{-3pt}
\item Designed and implemented the \textbf{Admin Dashboard} frontend for streamlined and efficient management.  
\vspace{-3pt}
\item Worked on \textbf{IP address discovery} within local networks, incorporating a \textbf{hot reload feature} for real-time updates.  
\vspace{-3pt}
\item Implemented \textbf{APIs} to enable network searches based on \textbf{IP addresses} and \textbf{software names}.  
\end{itemize}
% \vspace{2pt}
\resumeSubItem{Medical Diagnosis Application}{Personal Project \textbar{} \href{https://github.com/Anupam0401/Medical-Diagnosis-App}{Project link on GitHub}}
\vspace{-2pt}
\begin{itemize}
\item Developed a \textbf{Decision Tree Classifier} model to predict diseases based on patient symptoms.  
\vspace{-3pt}
\item Designed the model to identify and rank the top 10 most probable diseases based on input symptoms.  
\vspace{-3pt}
\item Created a user-friendly web application using \textbf{Streamlit} for seamless interaction and visualization.
\end{itemize}
% \vspace{2pt}
\resumeSubItem{Client Server Application}{Personal Project \textbar{} \href{https://github.com/Anupam0401/Client_Server_Application}{Project link on GitHub}}
\vspace{-2pt}
\begin{itemize}
\item Developed an \textbf{Echo Client-Server} application in Python for \textbf{Network Analysis}.  
\vspace{-3pt}
\item Integrated features like \textbf{File Viewing} and \textbf{Interactive Messaging} to enhance functionality.  
\vspace{-3pt}
\item Engineered the echo client-server to be \textbf{protocol independent} for broader applicability.  
\end{itemize}
\resumeSubHeadingListEnd
% \vspace{-5pt}
% \section{Publications}
% \resumeSubHeadingListStart
% \resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
% \vspace{2pt}
% \resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
% \resumeSubHeadingListEnd
\vspace{5pt}
%-----------Awards-----------------
\section{Achievements}
\begin{description}[font=$\bullet$]
\item {2022 \textbar{} Grand finalist in the Software category in \textbf{SIH 2022}.}
    \vspace{-5pt}
    \item {2022 \textbar{} Secured \textbf{Global Rank 2329} in Google Hash Code.}
    \vspace{-5pt}
    \item {2021 \textbar{} Secured \textbf{Global Rank 2436} in Google KickStart Round D.}
    \vspace{-5pt}
    \item {2019 \textbar{} \textbf{99 percentile} in JEE Mains/Advanced.}
    \vspace{-5pt}
    \item {2017 \textbar{} Achieved \textbf{Rank 1} in Darjeeling district in ICSE 10\textsuperscript{th} Board Exams.}

\end{description}

% \vspace{-5pt}
% \section{Volunteer Experience}
%   \resumeSubHeadingListStart
% 	\resumeSubheading
%     {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
%     {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
% \vspace{5pt}
%     % \vspace{10pt}\textbf{\large{Community Experience}}
%     \resumeSubheading
%     {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
%     {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}

% \resumeSubHeadingListEnd

\end{document}